---
title: "Correlation_Analysis"
author: "Yujia Gong"
date: "2023-08-18"
output: html_document
---

```{r}

library(readr)
library(dplyr)
data <- read_csv("Correlation_Analysis.csv")

```
# Calculate the mean and standard deviation of FE
```{r}

data$FE_avg <- rowMeans(data[, c("FE1", "FE2", "FE3")], na.rm=TRUE)
FE_avg_value <- mean(data$FE_avg, na.rm=TRUE)
FE_std_dev <- sd(data$FE_avg, na.rm=TRUE)
cat("Average of FE:", FE_avg_value, "\n")
cat("Standard Deviation of FE:", FE_std_dev, "\n")

```

# Calculate the mean and standard deviation of SI
```{r}

data$SI_avg <- rowMeans(data[, c("SI1", "SI2", "SI3", "SI4", "SI5")], na.rm=TRUE)
SI_avg_value <- mean(data$SI_avg, na.rm=TRUE)
SI_std_dev <- sd(data$SI_avg, na.rm=TRUE)
cat("Average of SI:", SI_avg_value, "\n")
cat("Standard Deviation of SI:", SI_std_dev, "\n")

```

# Calculate the mean and standard deviation of FH
```{r}

data$FH_avg <- rowMeans(data[, c("FH1", "FH2", "FH3")], na.rm=TRUE)
FH_avg_value <- mean(data$FH_avg, na.rm=TRUE)
FH_std_dev <- sd(data$FH_avg, na.rm=TRUE)
cat("Average of FH:", FH_avg_value, "\n")
cat("Standard Deviation of FH:", FH_std_dev, "\n")

```

# Calculate the mean and standard deviation of HS
```{r}

data$HS_avg <- rowMeans(data[, c("HS1", "HS2", "HS3")], na.rm=TRUE)
HS_avg_value <- mean(data$HS_avg, na.rm=TRUE)
HS_std_dev <- sd(data$HS_avg, na.rm=TRUE)
cat("Average of HS:", HS_avg_value, "\n")
cat("Standard Deviation of HS:", HS_std_dev, "\n")

```

# Calculate the mean and standard deviation of PEOU
```{r}

data$PEOU_avg <- rowMeans(data[, c("PEOU1", "PEOU2")], na.rm=TRUE)
PEOU_avg_value <- mean(data$PEOU_avg, na.rm=TRUE)
PEOU_std_dev <- sd(data$PEOU_avg, na.rm=TRUE)
cat("Average of PEOU:", PEOU_avg_value, "\n")
cat("Standard Deviation of PEOU:", PEOU_std_dev, "\n")

```

# Calculate the mean and standard deviation of PU
```{r}

data$PU_avg <- rowMeans(data[, c("PU1", "PU2", "PU3")], na.rm=TRUE)
PU_avg_value <- mean(data$PU_avg, na.rm=TRUE)
PU_std_dev <- sd(data$PU_avg, na.rm=TRUE)
cat("Average of PU:", PU_avg_value, "\n")
cat("Standard Deviation of PU:", PU_std_dev, "\n")

```

# Calculate the mean and standard deviation of CUB
```{r}

CUB_avg_value <- mean(data$CUB, na.rm=TRUE)
CUB_std_dev <- sd(data$CUB, na.rm=TRUE)
cat("Average of CUB:", CUB_avg_value, "\n")
cat("Standard Deviation of CUB:", CUB_std_dev, "\n")

```
# H1a: The fitness environment significantly impacts users' perceived ease of use of fitness apps.
```{r}

correlation_H1a <- cor.test(data$FE_avg, data$PEOU_avg, method="pearson")
print(correlation_H1a)

```
# H1b: The fitness environment significantly impacts users' perceived usefulness of fitness apps.
```{r}

correlation_H1b <- cor.test(data$FE_avg, data$PU_avg, method="pearson")
print(correlation_H1b)

```

# H1c: The fitness environment significantly impacts users' continuous use behaviour of fitness apps.
```{r}

correlation_H1c <- cor.test(data$FE_avg, data$CUB, method="pearson")
print(correlation_H1c)

```

# H2a: The social influence significantly impacts users' perceived ease of use of fitness apps.
```{r}

correlation_H2a <- cor.test(data$SI_avg, data$PEOU_avg, method="pearson")
print(correlation_H2a)

```

# H2b: The social influence significantly impacts users' perceived usefulness of fitness apps.
```{r}

correlation_H2b <- cor.test(data$SI_avg, data$PU_avg, method="pearson")
print(correlation_H2b)

```

# H2c: The social influence significantly impacts users' continuous use behaviour of fitness apps.
```{r}

correlation_H2c <- cor.test(data$SI_avg, data$CUB, method="pearson")
print(correlation_H2c)

```

# H3a: The fitness history significantly impacts users' perceived ease of use of fitness apps.
```{r}

correlation_H3a <- cor.test(data$FH_avg, data$PEOU_avg, method="pearson")
print(correlation_H3a)

```

# H3b: The fitness history significantly impacts users' perceived usefulness of fitness apps.
```{r}

correlation_H3b <- cor.test(data$FH_avg, data$PU_avg, method="pearson")
print(correlation_H3b)

```

# H3c: The fitness history significantly impacts users' continuous use behaviour of fitness apps.
```{r}

correlation_H3c <- cor.test(data$FH_avg, data$CUB, method="pearson")
print(correlation_H3c)

```

# H4a: The health status significantly impacts users' perceived ease of use of fitness apps.
```{r}

correlation_H4a <- cor.test(data$HS_avg, data$PEOU_avg, method="pearson")
print(correlation_H4a)

```

# H4b: The health status significantly impacts users' perceived usefulness of fitness apps.
```{r}

correlation_H4b <- cor.test(data$HS_avg, data$PU_avg, method="pearson")
print(correlation_H4b)

```

# H4c: The health status significantly impacts users' continuous use behaviour of fitness apps.
```{r}

correlation_H4c <- cor.test(data$HS_avg, data$CUB, method="pearson")
print(correlation_H4c)

```

# H5: Users' perceived ease of use of fitness apps positively impacts perceived usefulness.
```{r}

correlation_H5 <- cor.test(data$PEOU_avg, data$PU_avg, method="pearson")
print(correlation_H5)

```

# H6: Users' perceived ease of use of fitness apps positively impacts continuous use behaviour.
```{r}

correlation_H6 <- cor.test(data$PEOU_avg, data$CUB, method="pearson")
print(correlation_H6)

```

# H7: Users' perceived usefulness of fitness apps positively impacts continuous use behaviour.
```{r}

correlation_H7 <- cor.test(data$PU_avg, data$CUB, method="pearson")
print(correlation_H7)

```