---
title: "Variance Analysis"
author: "Yujia Gong"
date: "2023-08-18"
output: html_document
---

```{r}
library(dplyr)
data <- read.csv("VarianceAnalysis_Data.csv")
```

# Variance Analysis using PEOU as the dependent variable
# Fitness Environment
```{r}

data %>%
  group_by(FE) %>%
  summarise(Number = n(),
            Mean = mean(PEOU, na.rm = TRUE),
            StdDev = sd(PEOU, na.rm = TRUE))

aov_FE_POEU <- t.test(PEOU ~ FE, data = data, var.equal = TRUE)
print(aov_FE_POEU)

```


# Social Influence
```{r}

data %>%
  group_by(SI) %>%
  summarise(Number = n(),
            Mean = mean(PEOU, na.rm = TRUE),
            StdDev = sd(PEOU, na.rm = TRUE))

data$SI <- as.factor(data$SI)
aov_SI_POEU <- aov(PEOU ~ SI, data=data)
summary(aov_SI_POEU)

```

# Fitness History
```{r}

data %>%
  group_by(FH) %>%
  summarise(Number = n(),
            Mean = mean(PEOU, na.rm = TRUE),
            StdDev = sd(PEOU, na.rm = TRUE))

data$FH <- as.factor(data$FH)
aov_FH_POEU <- aov(PEOU ~ FH, data=data)
summary(aov_FH_POEU)

```

# Health status
```{r}

data %>%
  group_by(HS) %>%
  summarise(Number = n(),
            Mean = mean(PEOU, na.rm = TRUE),
            StdDev = sd(PEOU, na.rm = TRUE))

data$HS <- as.factor(data$HS)
aov_HS_POEU <- aov(PEOU ~ HS, data=data)
summary(aov_HS_POEU)

```

# Variance Analysis using PU as the dependent variable
# Fitness Environment
```{r}

data %>%
  group_by(FE) %>%
  summarise(Number = n(),
            Mean = mean(PU, na.rm = TRUE),
            StdDev = sd(PU, na.rm = TRUE))

aov_FE_PU <- t.test(PU ~ FE, data = data, var.equal = TRUE)
print(aov_FE_PU)

```

# Social Influence
```{r}

data %>%
  group_by(SI) %>%
  summarise(Number = n(),
            Mean = mean(PU, na.rm = TRUE),
            StdDev = sd(PU, na.rm = TRUE))

data$SI <- as.factor(data$SI)
aov_SI_PU <- aov(PU ~ SI, data=data)
summary(aov_SI_PU)

```

# Fitness History
```{r}

data %>%
  group_by(FH) %>%
  summarise(Number = n(),
            Mean = mean(PU, na.rm = TRUE),
            StdDev = sd(PU, na.rm = TRUE))

data$FH <- as.factor(data$FH)
aov_FH_PU <- aov(PU ~ FH, data=data)
summary(aov_FH_PU)

```

# Health status
```{r}

data %>%
  group_by(HS) %>%
  summarise(Number = n(),
            Mean = mean(PU, na.rm = TRUE),
            StdDev = sd(PU, na.rm = TRUE))

data$HS <- as.factor(data$HS)
aov_HS_PU <- aov(PU ~ HS, data=data)
summary(aov_HS_PU)

```

# Variance Analysis using CUB as the dependent variable
# Fitness Environment
```{r}

data %>%
  group_by(FE) %>%
  summarise(Number = n(),
            Mean = mean(CUB, na.rm = TRUE),
            StdDev = sd(CUB, na.rm = TRUE))

aov_FE_CUB <- t.test(CUB ~ FE, data = data, var.equal = TRUE)
print(aov_FE_CUB)

```

# Social Influence
```{r}

data %>%
  group_by(SI) %>%
  summarise(Number = n(),
            Mean = mean(CUB, na.rm = TRUE),
            StdDev = sd(CUB, na.rm = TRUE))

data$SI <- as.factor(data$SI)
aov_SI_CUB <- aov(CUB ~ SI, data=data)
summary(aov_SI_CUB)

```

# Fitness History
```{r}

data %>%
  group_by(FH) %>%
  summarise(Number = n(),
            Mean = mean(CUB, na.rm = TRUE),
            StdDev = sd(CUB, na.rm = TRUE))

data$FH <- as.factor(data$FH)
aov_FH_CUB <- aov(CUB ~ FH, data=data)
summary(aov_FH_CUB)

```

# Health status
```{r}

data %>%
  group_by(HS) %>%
  summarise(Number = n(),
            Mean = mean(CUB, na.rm = TRUE),
            StdDev = sd(CUB, na.rm = TRUE))

data$HS <- as.factor(data$HS)
aov_HS_CUB <- aov(PU ~ CUB, data=data)
summary(aov_HS_CUB)

```


